### 2025-05-06 paper/ecai2025/sects/discussion.tex
minor on discussion

In the following, we discuss the results obtained in \Cref{sect:experiments} and provide some insights into the performance of \fname{} compared to SHAC and PPO, addressing the research questions posed in \Cref{sect:introduction}. Note that \fname{} does not aim to outperform SHAC, but rather to perform comparably while being applicable even in non-differentiable environments.

>>>>

\section{Discussion}
In the following, we discuss the results obtained in \Cref{sect:experiments} and provide some insights into the performance of \fname{} compared to SHAC and PPO, addressing the research questions posed in \Cref{sect:introduction}. Note that \fname{} does not aim to outperform SHAC, but rather to perform comparably while being applicable even in non-differentiable environments.
